\section{Final Project}
\label{final-project}

In this part of the report, I will explain the project I developed in detail. I will divide the project into two parts: Back-end and Front-end.

For the final project, we were given some time to develop. We were first given time to develop after the \texttt{Spring} framework part. It was for developing the back-end. The second time given was after the \texttt{React} part. \texttt{React} part was finished on the second day of the fourth week. Since the main internship program was four weeks at OBSS, we were expected to finish the final project by the end of the fourth week. However, I could not complete the project at this time. Since my internship period was six weeks and I could not complete the project, they asked me to complete the project within this period.

In the fifth week of my internship, I decided to start from scratch as I thought that I made mistakes at many points while developing the project and that if I continued to develop on these mistakes, it would harm the development phase. First, I tried to find out where I lacked and made mistakes.

I tried to learn \texttt{React} from the beginning for three days because I thought I had problems with the \texttt{React} part. As a result of this work, I have come to a position where I can do many things on \texttt{React} without difficulty. I spent the next two days thinking about simple things and design. In my last week, I rebuilt and coded the entire project, starting from scratch.

\subsection{Project and Requirements}

The final project was a basic Book Portal whose requirements were provided. We were provided the \hyperref[book-portal]{document located in the appendicies} for basic requirements.

In my project, there are two main entities: User and Book. Each user has a role, admin or user role, and book lists for favorite and read books. Each book has many information about itself: name, author, type, publisher, and publication date. Both admins and users can log in to the system. Each admin is also a user and can do everything a user can, such as updating passwords, seeing books, adding books to their read or favorite lists, and searching for a book and its information. Additionally, an admin can add, update, and delete users and books.

\input{files/back-end.tex}

\input{files/front-end.tex}
